Crystals

### 2017-01-26 doc/ms.tex
Wrote some stuff that needs to be written...

\begin{table}
\centering
\begin{tabular}{|lll|}
\hline
{\bf Quantity}      &   {\bf Meaning}   &  {\bf Prior distribution}\\
\hline
{\em Hyperparameters} & &\\
$N_{\rm narrow}$   &   Number of narrow spikes    &  $\propto 1/(N_{\rm narrow}+1)$, $N_{\rm narrow} \in \{0, 1, ..., 300\}$ \\
$N_{\rm wide}$   &   Number of wide spikes    &  $\propto 1/(N_{\rm wide}+1)$,
$N_{\rm wide} \in \{0, 1, ..., 300\}$ \\
\hline
{\em Parameters}& &\\
$\sigma_0$ &    Constant noise level  &   $\ln(\sigma_0) \sim \textnormal{Laplace}(0,5)$\\
$\sigma_1$ &    Noise proportionality   &  $\ln(\sigma_1) \sim \textnormal{Laplace}(0,5)$ \\
$\nu$     &   Shape parameter for residuals   &   LogUniform$(1, 1000)$\\
$b$       & Mean background level       & $\ln(b) \sim$ Laplace$(0, 5)$\\
$\{n_1, ..., n_4\}$  & 
\hline
{\em Data}&&\\
\hline
$\{y_1, y_2, ..., y_n\}$  &   Measurements    & $t(f(x_i; \params), ,\nu)$\\
\hline
{\em Prior information}&&\\
\hline
$n$ & Number of measurements & given\\
$\{x_1, x_2, ..., x_n\}$  & $x$-values of measurements & given \\

\hline
\end{tabular}
\caption{\label{tab:priors}}
\end{table}

The shape of the model function $f(x)$ is therefore
\begin{align}
f(x) &= A + f_{\rm wide}(x) + \sum_{i=1}^N a_i f_i(x)
\end{align}
and the crystallinity is
\begin{align}
C &= \frac{\int f_{\rm wide}(x) \, dx}
          {\int f_{\rm wide}(x) \, dx + \int f_{\rm narrow}(x) \, dx}
\end{align}

>>>>

\begin{table}
\centering
\begin{tabular}{|lll|}
\hline
{\bf Quantity}      &   {\bf Meaning}   &  {\bf Prior distribution}\\
\hline
{\em Hyperparameters} & &\\
$N_{\rm narrow}$   &   Number of narrow spikes    &  $\propto 1/(N_{\rm narrow}+1)$, $N_{\rm narrow} \in \{0, 1, ..., 300\}$ \\
$N_{\rm wide}$   &   Number of wide spikes    &  $\propto 1/(N_{\rm wide}+1)$,
$N_{\rm wide} \in \{0, 1, ..., 300\}$ \\

\hline
{\em Parameters}& &\\
$\sigma_0$ &    Constant noise level  &   $\ln(\sigma_0) \sim \textnormal{Laplace}(0,5)$\\
$\sigma_1$ &    Noise proportionality   &  $\ln(\sigma_1) \sim \textnormal{Laplace}(0,5)$ \\
$\nu$     &   Shape parameter for residuals   &   LogUniform$(1, 1000)$\\
$b$       & Mean background level       & Laplace$(0, 5)$\\
$\{n_1, ..., n_4\}$  & Background deviations & iid Normal$(0,1)$\\
\hline
{\em Data}&&\\
\hline
$\{y_1, y_2, ..., y_n\}$  &   Measurements    & Student $t(f(x_i; \params), ,\nu)$\\
\hline
{\em Prior information}&&\\
\hline
$n$ & Number of measurements & given\\
$\{x_1, x_2, ..., x_n\}$  & $x$-values of measurements & given \\
\hline
\end{tabular}
\caption{\label{tab:priors}}
\end{table}

The Laplace, or biexponential, distribution with location parameter $a$ and
scale parameter $b$ has probability density
\begin{align}
p(x | a, b) &= \frac{1}{2b}\exp\left[-\frac{|x - a|}{b}\right].
\end{align}

The shape of the model function $f(x)$ is therefore
\begin{align}
f(x) &= f_{\rm bg}(x) + f_{\rm wide}(x) + f_{\rm narrow}(x)
\end{align}
and the crystallinity is
\begin{align}
C &= \frac{\int f_{\rm wide}(x) \, dx}
          {\int f_{\rm wide}(x) \, dx + \int f_{\rm narrow}(x) \, dx}
\end{align}
